### 2014-01-07 image_analysis_paper/plos_draft.tex
Added timing to draft

\begin{table}
	\begin{tabular}{| p{0.3\textwidth} | c | c | p{0.3\textwidth} |}
		\hline 
		Method & Spearman's $\rho$ & Execution Time & Notes About Method \\ 
		\hline 
		PCA on one-dimensional profiles & 0.9244 & & \\
		\hline 
		DMAPS on one-dimensional profiles & 0.9209 & & \\
		\hline 
		Angular synchornization + DMAPS on one-dimensional profiles & 0.9164 & & \\
		\hline 
		VDM on one-dimensional profiles & 0.9232 & & \\	
		\hline 
		VDM on two-dimensional images & 0.9051  & & \\
		\hline 	
		Scattering transform + DMAPS on two-dimensional profiles & 0.9011  & & \\
		\hline
	\end{tabular}
\end{table}
% You may title this section "Methods" or "Models".
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\section*{Materials and Methods}

>>>>

\begin{table}
	\begin{tabular}{| p{0.3\textwidth} | c | c | p{0.3\textwidth} |}
		\hline 
		Method & Spearman's $\rho$ & Execution Time & Notes About Method \\ 
		\hline 
		PCA on one-dimensional profiles & 0.9244 & < 1 second & \\
		\hline 
		DMAPS on one-dimensional profiles & 0.9209 & < 1 second & \\
		\hline 
		Angular synchornization + DMAPS on one-dimensional profiles & 0.9164 & < 1 second & \\
		\hline 
		VDM on one-dimensional profiles & 0.9232 & < 1 second & \\	
		\hline 
		VDM on two-dimensional images & 0.9051  & 325 seconds & \\
		\hline 	
		Scattering transform + DMAPS on two-dimensional profiles & 0.9011  & 86 seconds & \\
		\hline
	\end{tabular}
\end{table}
% You may title this section "Methods" or "Models".
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\section*{Materials and Methods}
